---
title: "Overlaying Plot"
output: html_document
---

```{r setup, include=FALSE}
# change figure resolution
knitr::opts_chunk$set(dpi=300)

# load packages
library(palmerpenguins)
library(ggplot2)
library(ggExtra)
library(GGally)
```

### Marginal distribution with ggExtra
```{r ggExtra, warning=FALSE}
scatter <- ggplot(data = penguins) +
  geom_point(aes(x = flipper_length_mm,
                 y = body_mass_g))

# marginal histogram
margin_densigram <- ggExtra::ggMarginal(scatter, 
                                        type = "densigram",
                                        fill = "slateblue")

margin_densigram
```

### Boxplot with jitter
```{r Boxplot, warning=FALSE}
boxplot_jitter <- ggplot(data = penguins,
                         aes(x = species,
                             y = bill_length_mm)) +
  geom_boxplot() +
  geom_jitter()

boxplot_jitter
```

### Scatter plot with rug
Adding rug gives insight about variable distribution
```{r rug, warning=FALSE}
rug <- ggplot(data = penguins,
              aes(x = flipper_length_mm,
                  y = body_mass_g)) +
  geom_point() +
  geom_rug(col="steelblue",
           alpha=0.1, 
           size=1.5)

rug
```

### Scatter plot with linear model and confidence interval
The `method` argument allows to apply different smoothing method like glm, loess and more. 
```{r lm, warning=FALSE}
lm <- ggplot(data = penguins,
             aes(x = flipper_length_mm,
                 y = body_mass_g)) +
  geom_point() +
  geom_smooth(method=lm,
              formula = y ~ x,
              color="red", 
              fill="#69b3a2", 
              se=TRUE)

lm
```

### Scatterplot matrix with ggpairs
Scatter plots of each pair of numeric variable are drawn on the left part of the figure. Pearson correlation is displayed on the right. Variable distribution is available on the diagonal.
```{r ggpairs, warning=FALSE}
# create dataframe with numeric values
penguins_num <- penguins %>% 
  dplyr::select(bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g)

ggpairs(penguins_num) 
```

### Scatter plot with line plot
```{r line, warning=FALSE}
# create dataframe with numeric values
penguins_mean <- penguins %>% 
  dplyr::group_by(year) %>% 
  dplyr::summarise(body_mass_mean = mean(body_mass_g, na.rm = TRUE))

line <- ggplot(data = penguins_mean,
               aes(x = year,
                   y = body_mass_mean)) +
  geom_point() +
  geom_line()

line
```

